---
title: 'Organisations Lab 2'
author: "Your Name"
date: "The Date"
output:
  html_document:
    df_print: paged
fontsize: 12pt
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse) 
library(knitr)
library(kableExtra)
library(datasauRus)

# Load any additional packages you used in the homework
# Never install packages in your RMarkdown file!

```




## Exercise 1: Using HELP

Based on the help file, how many rows and how many columns does the datasaurus_dozen file have? What are the variables included in the data frame? Now observe various summary statistics of each data-set (see explanation below). What do you notice? Add your responses to your lab report.

ANSWER: YOUR ANSWER HERE (NO NEED TO CODE)



## Exercise 2: Plots

Choose four different datasets from datasaurus_dozen, and create a plot for each of the four datasets.

ANSWER: YOUR ANSWER HERE 


```{r plots}

# This is the code-chunk, where you write your code 

```



## Exercise 3: Summary statistics

Create a table with summary statistics for each of the four datasets. You will have a row for each dataset, and a column for each summary statistics, consisting of the means of x and y, the standard deviations of x and y, the correlation between x and y and the sample size. To create the table - you can use the code below and adapt it!



```{r summary-stats}

# This is the code-chunk, where you write your code 

```




## Exercise 4: Using facets

Now we will plot the y vs. x for all the datasets contained in `datasaurus_dozen` using facets. Facet iterates through the dataset variable, placing the plots in a 3 column grid. Make sure to configure the size of the diagram by adding options in your code-chunk using the cog-wheel.



```{r using-facets}

# This is the code-chunk, where you write your code 

```



## Exercise 5: Draw my data

Finally: use the [DrawMyData](http://robertgrantstats.co.uk/drawmydata.html) tool, to create your own drawing. From this drawing you can extract the dataset. Plot the dataset using ggplot and calculate the correlation as before.



```{r draw-data}

# This is the code-chunk, where you write your code 


```

